\documentclass{article}

% Language setting
% Replace `english' with e.g. `spanish' to change the document language
\usepackage[english]{babel}

% Set page size and margins
% Replace `letterpaper' with `a4paper' for UK/EU standard size
\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

\title{Research Report\\Network Encryption and Traffic Analysis}

\author{Edoardo Arturo Cancelli -- s335716\\
Francesca Malagodi -- s336645}

\begin{document}
\maketitle

\begin{abstract}
Your abstract.
\end{abstract}
%Introduction
%Background
%➢ Overview of the problem/evaluation
%➢ Examples (where applicable)
%➢ Discussion about mitigations/protections/applications
%➢ Conclusion

\section{Introduction}


\section{Background}
\subsection{The evolution of encryption}
Encryption is the process of turning the original plain 
message into cipher text, an unrecognisable message 
different from the starting one.
The reverse of encryption is decryption, and the entire 
process is called cryptography. In general cryptography
focuses on privacy and the security of information based 
on data integrity, confidentiality and authentication. \cite{journal33}
\\To secure the exchange of information over the Web, the HTTPS
protocoll has been created to provide a cryptographic protection. 
HTTPS is based on other protection protocls that have been improved;
it basically runs the HTTP protocol, which is at the center of the Web but does 
not provide confidentiality or integrity, on top of cryptography protocols, such as SSL and TLS,
that allow bidirectional encryption in communication. 
\\ Because of the very different levels of security, it is believed 
that the HTTPS will replace mostly HTTP protocols, also thanks to
initiatives and actions taken by the major browser vendors to 
promote the importance of security. \cite{postcards}
\section{Overview of the problem/evaluation}

\section{Examples}

\section{Discussion about mitigations/protections/applications}

\section{Conclusion}


\begin{thebibliography}{1}
    \bibitem{journal33}
    K. John Singh and R. Manimegalai (2015), Evolution of Encryption Techniques and Data Security Mechanisms,
    World Applied Sciences Journal 33 (10): 1597-1613.
    \bibitem{postcards}
    S. Calzavara, R. Focardi, M. Nemec, A. Rabitti and M. Squarcina, "Postcards from the Post-HTTP World: Amplification of HTTPS Vulnerabilities in the Web Ecosystem," 2019 IEEE Symposium on Security and Privacy (SP), San Francisco, CA, USA, 2019, pp. 281-298.
\end{thebibliography}

\end{document}
