%!TEX root = ../main.tex
\section{Background}
\subsection{The evolution of encryption}
Encryption is the process of turning the original plain 
message into cipher text, an unrecognizable message 
different from the starting one.
The reverse of encryption is decryption, and the entire 
process is called cryptography. In general cryptography
focuses on privacy and the security of information based 
on data integrity, confidentiality and authentication. \cite{journal33}
\\To secure the exchange of information over the Web, the HTTPS
protocol has been created to provide a cryptographic protection. 
HTTPS is based on other protection protocols that have been improved;
it basically runs the HTTP protocol, which is at the center of the Web but does 
not provide confidentiality or integrity, on top of cryptography protocols, such as SSL and TLS,
that allow bidirectional encryption in communication. 
\\ Because of the very different levels of security, it is believed 
that the HTTPS will replace mostly HTTP protocols, also thanks to
initiatives and actions taken by the major browser vendors to 
promote the importance of security. \cite{postcards}

\subsection{Protocols}
As it is briefly explained in the paragraph above there are different protocols 
that contribute to security on the Web. The two more widely used are TLS (Transport Layer Security) and IPsec (Internet Protocol Security).
\subparagraph*{TLS} aims to ensure end-to-end security protection against active attacks, 
it is a protocol that runs between a client and a server. In the
beginning it was only used in web browsers for HTTPS connections, now it is used on
a wider scale: e-commerce transactions, VPNs, and mobile apps for Android and iOS. 
It consists of the Handshake Protocol, which focus is on key establishment and authentication, 
and the Record Protocol, which allows a secur delivery of the data. TLS has been the 
subject of many research analysis in orderd to establish its level of security. If on
the one hand, the Record Protocol has been demonstrated to be a secure encryption in many studies,
the Handshake Protocol still has some flaws. The main weakness is the interaction between 
the Handshake and the Record protocols: the application key is used to encrypt the last two messages
of the Handshake Protocol. \cite{tls}

\subparagraph*{IPsec} is a network protocol that permits the encryption and authentication of
data at the IP layer, regardless of the kind of data or function that is being transmitted. 
In a 1999 evaluation \cite{ferguson1999cryptographic} quite a few critisims were brought up on the 
process and the results of IPsec. The disappointment on how it was developed was a shared opnion among
the people involved in it. But even with the critics it was the best IP security protocol available, 
in comparison to all the protocols in the market, IPsec seemed to be one with the better performance. 
Their main critisism was its complexity; it had too many options and too much flexibility, this results 
in an important weakness when it comes to security. Another critic was raised one encryption and authentication,
it needs to be applied to all the data that can be used to determine the meaning of a packet, 
authentication needs to be applied to the ciphertext but also to the decryption key. 


\subsection{The metadata}
(What encryption leaves behind: packet sizes, time stamps, directional flow, and IP routing information.)
In the paragraphs above have been analised some ways to encrypt data when exchanged between two or more parties, 
however some data still needs to be protected: the metadata. A lot of information can be leaked trough 
data records and association, which is why limiting access and data masking becomes as important as ecncryption. 
The access to the data needs to be controlled trough access requests which are checked and then granted or denied 
depending on the outcome of the controls. Other tecniques used are disassotiations tecniques which permit the anonymity 
of the user and its depersonalizations to maintain privacy. Sometimes instead of anonymization, which is a non-reversible process, 
it is used psedonymination, which is a similar tecnique but the original identifying information is not deleted but only 
separeted from the data, which is not associated to the pseudonym. Another way to shield sensitive data is encryption again, 
in this case the key is initially possessed only by the owner. 
\cite{6149189}


%\subsection{Network packets} 
%The data is sent over computers into packets, which are a small part of a bigger message. 
%Every packet consists of two parts: the header and the payload. 
%The header is like a label, it provides information about the contents and the origin and destination's IP addresses. 
%The payload is the actual data.
%The way data is shared is important to detect attacks and suspicious activity.
